A Technique for Inter-Catalogue Recommendations

### 2014-06-11 paper2/paper.tex
Edits to Data section

\section*{Data}
For this work, we utilize most of the product catalogue of Macy's as presented
at www.macys.com. This catalogue consists of numerous categories of mostly
apparel, each of which includes hundreds to thousands of items. We confine this
study to the 49 categories within the two main parent categories ``Men'' and
``Women'' that contain at least 200 items that are associated to multiple
brands. In total, this dataset consists of 66,071 items in 49 categories with
some items listed in multiple categories. For each item we record its
description, all categories within which it is listed, and its associated
recommendations. By {\em recommendations}, we are referring to the items---there
are typically four in the case of Macy's---that are displayed on a product's
details page under the heading ``Customers Also Shopped''. The presence of these
recommendations implicitly forms a directed graph over the product catalogue, in
which the nodes are the {\em products} or {\em items} and the edges are the {\em
recommendations}. We call these types of graphs {\em recommendation graphs} and
they play a central role in this study.

>>>>

\section*{Data}
For this work, we utilize most of the product catalogue of Macy's as presented
at www.macys.com. This catalogue consists of numerous categories, which are
mostly apparel. Each category includes hundreds to thousands of items. We
confine this study to the 49 categories under the two main parent categories
``Men'' and ``Women'' that contain at least 200 items from multiple brands.  In
total, this dataset consists of 66,071 items in 49 categories with some items
listed in multiple categories. For each item we record its description, all
categories within which it is listed, and its associated recommendations. By
{\em recommendations}, we are referring to the items---there are typically four
in the case of Macy's---that are displayed on a product's details page under the
heading ``Customers Also Shopped''. The presence of these recommendations
implicitly forms a directed graph over the product catalogue, in which the nodes
are the {\em products} or {\em items} and the edges are the {\em
recommendations}. We call these types of graphs {\em recommendation graphs} and
they play a central role in this study.
